---
title: "KmeansR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{KmeansR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Kmeans)
```
## Introduction to the Kmeans Package
This document introduces you to the Kmeans package. This is different from the Kmeans package available in base R. This package is created as a part of a course project to learn the fundamentals of collborative software development. 
This package implements the K-Means algorith for clustering. This will work on any dataset with valid numerical features, and includes fit, predict, and cluster_summary functions, as well as as elbow and silhouette methods for hyperparameter “k” optimization


## Data
To explore the Kmeans package, we will use the iris dataset. This dataset contains features from 4 different variesties of Iris flowers. This is a classical dataset for classification. Let's explore how to cluster this dataset using the Kmeans package.

```{r data}
data <- iris
head(data)
dim(data)
```

## Fit the data set using `fit()`

```{r fit}
fit(data, k=3, n_init = 1, max_iter = 10)
```
