---
title: "KmeansR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{KmeansR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Kmeans)
```
## Introduction to the Kmeans Package
This document introduces you to the Kmeans package. This is different from the Kmeans package available in base R. This package is created as a part of a course project to learn the fundamentals of collborative software development. 
This package implements the K-Means algorith for clustering. This will work on any dataset with valid numerical features, and includes fit, predict, and cluster_summary functions, as well as as elbow and silhouette methods for hyperparameter “k” optimization


dplyr’s basic set of tools, and shows you how to apply them to data frames. dplyr also supports databases via the dbplyr package, once you’ve installed, read vignette("dbplyr") to learn more
