---
title: "KmeansR-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{KmeansR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Kmeans)
library(tidyverse)
```
## Introduction to the Kmeans Package
This document introduces you to the Kmeans package. This is different from the Kmeans package available in base R. This package is created as a part of a course project to learn the fundamentals of collborative software development. 
This package implements the K-Means algorith for clustering. This will work on any dataset with valid numerical features, and includes fit, predict, and cluster_summary functions, as well as as elbow and silhouette methods for hyperparameter “k” optimization


## Data
To explore the Kmeans package, we will use the iris dataset. This dataset contains features from 4 different variesties of Iris flowers. This is a classical dataset for classification. Let's explore how to cluster this dataset using the Kmeans package.

```{r data}
x1 <- rnorm(5, 1, 0.2)
x2 <- rnorm(5, 2, 0.2)
x3 <- rnorm(5, 3, 0.2)
x <- c(x1, x2, x3)
y <- c(x2, x1, x1)

X_train <- data.frame(x, y)
```

## Fit the data set using `fit()`
Let's fit using the Iris data to get the labels and centers.

```{r fit}
km <- fit(X_train, k = 2)
labels <- km$labels
centers <- km$centers
print("Cluster centers are: ")
centers
print("Labels are : ")
labels
```

## Predict 
Let's use the kmeans algorithm to predict the label of an Iris flower
```{r predict}
X_new <- X_train[10, ]

# Make prediction
predict(X_new, centers)
```
```{r elbow}
centers <- c( 1, 2, 3, 4, 5, 6)
el <- elbow(X_train, centers)
inertia <- el$inertia
plot <- el$plot
plot
 
```


```{r silhouette}
centers <- c( 1, 2, 3, 4, 5, 6)
sl <- silhouette(X_train, centers)
scores <- sl$scores
plot <- sl$plot
plot
```


